Powering Hidden Markov Model by Neural Network based Generative Models

### 2019-10-13 manuscript/main.tex
capitalize introduction
for arxiv

\title{Powering Hidden Markov Model by Neural Network based Generative Models}
% \author{
%   Dong Liu$^{\dagger}$, Antoine Honoré$^{\ast \dagger}$, Saikat Chatterjee$^{\dagger}$, and Lars~K. Rasmussen$^{\dagger}$\\
%   $^{\dagger}$KTH Royal Institute of Technology, Stockholm, Sweden \\
%   $^{\ast}$Karolinska Institute, Stockholm, Sweden \\
%   E-mail: \{doli, honore, sach, lkra\}@kth.se}
\author{
  Author1, Author2, Author3, and Author4}

% \name{
% Dong Liu,
% Minh Thành Vu,
% Saikat Chatterjee,
% and Lars~K. Rasmussen
% }

%   \address{
%   KTH Royal Institute of Technology, Stockholm, Sweden \\
%   E-mail: \{doli, mtvu, sach, lkra\}@kth.se}

@@

\section{introduction}
Sequential data modeling is a challenging topic in pattern recognition and machine learning. For many applications, the assumption of independent and identically distributed (i.i.d.) data points is too strong to model data properly. Hidden Markov model (HMM) is a classic way to model sequential data without the i.i.d. assumption. HMM has been widely used in different practical problems, including applications in reinforcement learning \cite{ding2018reinforcementhmm,levine2018reinforcementReview}, natural language modeling \cite{khan2016survey,Hariyanti_2019}, biological sequence analysis such as proteins \cite{ASHWIN20172} and DNA \cite{ren2015dna}, etc.

>>>>

\title{Powering Hidden Markov Model by Neural Network based Generative Models}
\author{
  Dong Liu$^{\dagger}$, Antoine Honor\'e$^{\ast \dagger}$, Saikat Chatterjee$^{\dagger}$, and Lars~K. Rasmussen$^{\dagger}$\\
  $^{\dagger}$KTH Royal Institute of Technology, Stockholm, Sweden \\
  $^{\ast}$Karolinska Institute, Stockholm, Sweden \\
  E-mail: \{doli, honore, sach, lkra\}@kth.se}
% \author{
%   Author1, Author2, Author3, and Author4}

@@

\section{Introduction}
Sequential data modeling is a challenging topic in pattern recognition and machine learning. For many applications, the assumption of independent and identically distributed (i.i.d.) data points is too strong to model data properly. Hidden Markov model (HMM) is a classic way to model sequential data without the i.i.d. assumption. HMM has been widely used in different practical problems, including applications in reinforcement learning \cite{ding2018reinforcementhmm,levine2018reinforcementReview}, natural language modeling \cite{khan2016survey,Hariyanti_2019}, biological sequence analysis such as proteins \cite{ASHWIN20172} and DNA \cite{ren2015dna}, etc.
